\documentclass[pldi]{sigplanconf}

% \newcommand{\ignore}[1]{}

%% =============================================================
\def\tool{\textsc{Clotho}\xspace}
%\def\papertitle{\tool: Program Repairing using Exception Types, Constraint
%Automata and Typestate}
\def\papertitle{\tool: Saving Programs from Malformed Strings and Incorrect
String-handling}
\def\pdfauthors{}
\def\paperkeywords{}
%% =============================================================

\input{preamble}

\begin{document}

\title{\Large \bf \papertitle}

\authorinfo{Aritra Dhar \and Rahul Purandare}
{Indraprastha Institute of Information Technology Delhi}
{\{aritra1204,suresh1314,purandare\}@iiitd.ac.in}
\authorinfo{Mohan Dhawan}
{IBM IRL}
{mohan.dhawan@in.ibm.com}
\authorinfo{Suresh Rangnathan}
{Indraprastha Institute of Information Technology Delhi}
{suresh1314@iiitd.ac.in}

\maketitle



\begin{abstract}
\small
%marker
%\textcolor{red}{\textbf{Changes done}}\newline

%Runtime Exceptions are common types of exceptions which may lead to system
%crash
%which leads to shutdown or restart. For may critical application such scenario
%is unacceptable due to their nature which requires availability of the
%service. 
%Runtime exceptions may even leads to inconsistency of data in the system which
%may leads to further complications and expensive fixes.
%Program bugs which causes runtime exceptions often go unnoticed at the time of
%development as these exceptions are unchecked exceptions. The key issue is to
%guide the program through some exception suppression procedure which will leads
%the program to a consistent state hence improve the chance of surviving a fatal
%crash. Here we consider such programs for which restart is not an option.

Programs are susceptible to malformed data coming from untrusted sources.
Occasionally the programming logic or constructs used are inappropriate to
handle all types of constraints that are imposed by legal and well-formed data.
As a result programs produce unexpected results or even worse, they may crash.
Program behavior in both of these cases would be highly undesirable.

In this paper, we present a novel hybrid approach that saves programs from
crashing when the failures originate from malformed strings or inappropriate
handling of strings. Our approach statically analyses a program to identify
statements that are vulnerable to failures related to associated string data. It
then generates patches that are likely to satisfy constraints on the data, and
in case of failures produce program behavior which would be close to the
expected. The precision of the patches is improved with the help of a dynamic
analysis. The patches are activated only after a failure is detected, and the
technique incurs no runtime overhead during normal course of execution, and
negligible overhead in case of failures.

We have experimented with \java\ \code{String} API and applied \tool\ to $x$
hugely popular open-source libraries involving over $y$ million lines of
code to patch $z$ high priority bugs.
% that a few commonly used \java\ APIs.
Our evaluation shows that \tool\ is both practical and effective. The comparison
of the patches generated by our technique with the actual patches developed by
the programmers in the later versions shows that they are semantically similar.

%In this paper, we present a novel technique to recover from unexpected runtime
%exceptions. We have used hybrid of two techniques for efficient detection of
%potential point of failure and patch it closest to that to minimize the
%damage. 
%One technique uses type of runtime exception to apply appropriate patch. The
%other technique analyze the constraint information both statically and
%dynamically to produce patch which will have characteristics as the good
%values.
%Both of the techniques are followed by a taint analysis phase which will
%determine which program statements are safe to patch.

%We have experimented on \java\ \code{String} API and applied our patching
%techniques to some major bugs on some third party \java\ APIs and validate the
%patches with the actual patches developed by the programmers in the later
%versions.

\end{abstract}

% \terms
% Reliability, Languages 
% 
% \keywords
% program repair, runtime exception, software patching, symbolic execution,
% static
% analysis, type-state
\category{D.3.3}{Programming Languages}
{Language Constructs and Features}
[Control structures]

\keywords
Automatic Program Repairing, Runtime Exceptions,  Hybrid Program Analysis,
Strings

\input{sections/Introduction}
\input{sections/Motivation}
%\input{sections/ProblemFormulation}
%\input{sections/TaintAnalysis}
%\input{sections/BoundedAnalysis}
%\input{sections/RepairingStrategyConstrainAutomata}
\input{sections/newDesign}
\input{sections/Implementation}
\input{sections/Results}
\input{sections/RelatedWork}
\input{sections/Conclusion}

%%\acks

\raggedright
\small
\bibliographystyle{abbrvnat}
\bibliography{paper}

\end{document}
