\section{Motivation and Overview}
\label{sec:motivation}

Ensuring correctness for a software application is undecidable and static
analysis will invariably produce numerous
false positives. Moreover, programming logic can be
very complex and data coming from
external sources can be diverse. As result,  successful execution of a
real application cannot be guaranteed and unexpected failures may
happen. These failures often result in
runtime exceptions being thrown
by the applications which are generally not handled. The cost of these runtime
failures can vary depending on the criticality
of the applications which can be very high for mission-critical applications.

\java\ applications are typically built using libraries and 
\code{String} APIs are commonly used in libraries. Common and diverse usage
of strings in programs is known to be a significant source of errors \ref{}. In order to understand common
types of exceptions thrown in case of failures, we mined
the post repository on \texttt{stackoverflow}~\cite{stackoverflow}.
The most prominent exception types with the percentage share of higher than 5\%
are enumerated in Table~\ref{tab:stackoverlow}. The second column indicates
the types of exceptions, whereas the third column indicates their overall
percentage share. We observe that strings can play
a role in generating all except \code{SecurityException}. This result coupled
with the potentially heavy cost of program
crashes motivated us to develop on-the-fly repairing support for \java\ programs
regarding failures related to \code{String} APIs.


\begin{table}[t]
\scriptsize
\centering
\begin{tabular}{l|r|r}
\hline
\multicolumn{1}{c|}{\textbf{Runtime Exception Type}} &
\multicolumn{1}{c|}{\textbf{Frequency}} & \multicolumn{1}{c}{\textbf{\%}}\\
% \scalebox{0.83}
% {
\hline
\code{NullPointerException} & $34912$ & $54.94$ \\
\code{ClassCastException} & $7504$ & $11.81$ \\
\code{IndexOutOfBoundsException} & $6637$ & $10.44$ \\
\code{SecurityException}  & $5818$ & $9.15$ \\
\hline
\end{tabular}
\caption{Prominent runtime exceptions from stackoverflow~\cite{stackoverflow}.}
\label{tab:stackoverlow}
% }
\end{table}

\ignore{
\subsection{Problem and Challenges}
\label{subsec:problem}

In this work, we present a technique which automatically repairs programs
that otherwise would crash due to failures related to malformed strings or incorrect handling of
the string.  The technique i) identifies
the statements which might be vulnerable to string-related errors,
and are less critical to the functionality of the application such that
suboptimal behavior might be acceptable, ii) operates in non-invasive mode by ensuring no
side-effects during normal program execution and activating patches only when
the program is guaranteed to crash, iii) generates patches, iv) optimizes the number of
statements to be patched,  v) keeps program behavior as close as possible to the
intended behavior, and vi) incurs no runtime overhead during normal program execution
and only negligible overhead in case of failures.
}


\ignore{
In this work, we present a technique and its implementation to automatically repair programs
that otherwise would crash due to failures related to malformed strings or incorrect handling of
the string.  The technique i) identifies
the statements which might be vulnerable to string-related errors,
and are less critical to the functionality of the application such that
suboptimal behavior might be acceptable, ii) operates in non-invasive mode by ensuring no
side-effects during normal program execution and activating patches only when
the program is guaranteed to crash, iii) generates patches by identifying constraints on the string
data and if required, tweaks \code{String} API  parameters to regenerate legally correct
string data, iv) optimizes the number of statements to be patched by retaining only the ones that need to
be protected,  v) keeps program behavior as close as possible to the
intended behavior by developing precise patches, and vi) incurs no runtime
overhead during normal program execution and only negligible overhead in case of
failures.
}


\subsection{Overview}
\label{subsec:overview}

\ignore{
In order to achieve the goals enumerated in \xref{subsec:problem}, we
develop
several techniques which are outlined below.

\paragraph{Identifying Program Statements.} We perform static taint analysis
to identify sensitive data which are leaving the system via database, network
stream, file stream or console. Providing patches to the
statements that manipulate this data would be undesirable, since
activation of the patches in case failures may allow altered sensitive data to eventually
reach users. Hence, we only mark those program statements which do 
not manipulate these data.

\ignore{We have used \soot\ \infoflow\ framework
for static taint analysis. We have defined potential taint source and sinks in
the
configuration file. The \infoflow\ frameworks returns all the program
statements which lies in any of the program path from source and sink. We tag
these
statements as unsafe to patch.}

\paragraph{Noninvasive Patching.} In case a runtime exception that is thrown
by a statement as a result of a failure is already caught and handled in a
program,
we skip that statement from patching to avoid interfering with the results. Such
statements are identified by analyzing call-graphs and ensuring that no caller
method
in the call-chain handles the exception or its superclass. By embedding the
patches inside
\texttt{catch} blocks, we ensure that they do not get activated during normal
program execution.

\paragraph{Patch Generation.} We first perform an
intra-procedural static analysis
to identify constraints on the string objects under consideration. By identifying
the type of exceptions that can be thrown in case of a failure, we
develop patches that
regenerate string objects by tweaking \java\ \code{String} API used in
the statements to regenerate legal string objects and by trying to solve the
constraints. In the latter case,
we evaluate the constraints statically if complete information is available at
the compilation-time. Otherwise, the analysis automatically generates
code that performs dynamic analysis to solve the constraints, and then
inserts this code in the generated patches.

\paragraph{Optimizing Instrumentation.} We perform reaching definitions
analysis to skip marked statements
if the string variables that are contained in the statements are already
patched, and the variables
are not redefined along any path that originates from the patched statement.
This analysis reduces
instrumentation points in a program.

\paragraph{Patch Precision.} The precision of a program patch is improved,
firstly, by targeting only strings
for patching which allows us to develop more specialized patches, secondly, by
patching programs very
close to the points of potential failures which avoids unnecessary patching of other
unaffected variables and their potential
side effects, thirdly, by analyzing the types of exceptions that can be thrown which
provides valuable insights into
origins of failures, and finally, by considering all the constraints
on the strings. This would result
in a program behavior closed to the intended one in case of a failure.

\paragraph{Reduced Overhead.} The side-effect of non-invasive patches is that
they do not interfere during
normal execution which results in no runtime overhead. Even when they get
activated in case of failures,
they still cause negligible overhead since we perform no analysis during runtime
except if required resolve the dynamic constraints.
As our study reveals~\xref{sec:evaluation} the constraints are typically few and simple, making
the dynamic analysis light-weight.
}
	

\lstset{language=Java, caption=Example from \code{fileUtils} of Apache Commons
Library , label = snippet:exampleRepairing2}
\begin{figure}[t]
\centering
\begin{lstlisting}
public static String getPathNoEndSeparator
        (String filename) {
  return doGetPath(filename, 0);
}
private static String doGetPath
        (String filename, int separatorAdd) {
  if(filename == null) return null;
  int prefix = getPrefixLength(filename);
  if (prefix < 0) return null;
  int index = indexOfLastSeparator(filename);
  if ((prefix >= filename.length()) || (index < 0))
        return "";
  return filename.substring(prefix,
        index + separatorAdd);
}
\end{lstlisting}
\end{figure}

We give an overview of the techniques described in \xref{subsec:overview}
with the help of
an example in Code~\ref{snippet:exampleRepairing2}. The snippet depicts
some code
from \code{fileUtils} class of Apache Common IO library. The method
\code{getPathNoEndSeparator()} throws
a \code{StringIndexOutOfBounds} exception on Windows OS which originates from
statement 
\code{return filename.substring(prefix, index + separatorAdd)} on
line 13 when the method is called with parameter \code{"/foo.xml"}.  Here, the
value of \code{prefix} as
returned by the method \code{getPrefixLength} is 1 which fails to satisfy the
invariant
\code{prefix <= index + separatorAdd} for \code{substring} method. This results
in the exception being thrown.


\lstset{language=Java, caption=Patch for the \code{fileUtils}
in Apache Commons Library bug, label = snippet:exampleRepairing3, firstnumber
=13}
\begin{figure}[t]
\centering
\begin{lstlisting}
String temp = null;
try {
  temp = filename.substring(prefix, index + separatorAdd);
} catch(IndexOutOfBoundsException ex) {
  int length = filename.length;
  int t = index + separatorAdd;
  temp = filename.substring(
    getStart(prefix,t,length), getEnd(prefix,t,length));
}
return temp;
\end{lstlisting}
\end{figure}


Code~\ref{snippet:exampleRepairing3} presented the patch automatically
generated by \tool\
using our approach. By performing taint analysis, \tool\ identifies that statement 13 in
Code~\ref{snippet:exampleRepairing2}
can be vulnerable to a failure and it might throw \code{IndexOutOfBoundsException}
or  \code{NullPointerException}
which are not handled by any of its callers in the call-chain.
\tool\ then tries to capture constraints on the involved variable \code{filename}.
The only constraint on \code{filename} is \code{!(filename == null)} which is completely
static indicating that providing a patch to deal with \code{NulPointerException} is
not required. With a priori understanding of exception types and the invariants,
associated with them the tool then only creates a patch for \code{IndexOutOfBoundsException}
tweaking the API parameters as guided by the invariants to regenerate strings.
As a result, \tool\ replaces statement 13 with the code depicted in Code~\ref{snippet:exampleRepairing3}. The statement 17 shows
two methods namely \code{getStart} and \code{getEnd}
which compute legally correct bounds required by \code{substring} method to satisfy the invariant
\code{prefix <= index + separatorAdd}. Using these bounds \code{substring}
regenerates the string referenced by variable \code{temp}. 

The actual patch provided by the developers is semantically similar to the one
developed by \tool\ and both versions
of the code generate exactly the same output. Similarly, the patch developed 
by \tool\ for the bug depicted in Code~\ref{snippet:exampleRepairing1}
is semantically similar to the actual one provided by the developers and is presented in
Code~\ref{snippet:exampleRepairing4}. Here the object referenced by the string
variable \code{temp} is regenerated after adjusting the offset and ensuring that the invariant \code{offset <= length}
is not violated.

\lstset{language=java, caption=Patch for the Appache Log4j bug,
label = snippet:exampleRepairing4, firstnumber =4}
\begin{figure}[t]
\centering
\begin{lstlisting}
try {
    temp = new String(chars, offset, length);
} catch(StringIndexOutOfBoundsException ex) {
    int i = chars.length;
    temp = new String(chars,
        IndexRepair.getStart(offset, length, i),
            IndexRepair.getEnd(offset, length, i));
}
priorVariables.add(temp);
\end{lstlisting}
\end{figure}

We present in detail the techniques and the algorithms used in our analysis that
can produce patches to regenerate string variables under more
complex scenarios in \xref{sec:architecture} . Our study presented in
\xref{sec:evaluation} suggests that majority
of the string generation scenarios in practice are less complex.





















\ignore{
\subsection{Historical Context}
\label{subsec:historicalContext}

In recent past, we have seen couple of disastrous failure of critical military
and civilian infrastructure system due to system failure/crash which is results
of some very common runtime exceptions.

\begin{mylist}
  
  \item In USS Yorktown, complete failure in propulsion and navigation system by
  a simple divide-by-zero exception in flight deck database.
  
  \item AT\&T telephone network failure causing by one faulty switch causing ATC
  commutation blackout.
  
  \item Air-Traffic Control System in LA Airport lost communication with all 400
  airplanes caused by a system crash triggered by integer (32bit) overflow.
  
  \item Mars rover curiosity B-side computer memory overflow causing OS suspend
  and multiple restart.
  
  \item Trans-Siberian Gas Pipeline Explosion in 1982 by deliberate bugs in
  software controlled valves.
  
  \item Near-blackout of the national grid in Austria caused by faulty function
  call.
  
  
\end{mylist}


\subsection{Data from Stack Overflow Posts}
\label{subsec:stackoverflow}

\begin{table}[t]
\small
\begin{tabular}{l|r|r}
\multicolumn{1}{c|}{\textbf{Runtime Exception Type}} &
\multicolumn{1}{c|}{\textbf{Frequency}} & \multicolumn{1}{c}{\textbf{\%}}\\
% \scalebox{0.83}
% {
\hline
\code{NullPointerException} & $34912$ & $54.94$ \\
\code{ClassCastException} & $7504$ & $11.81$ \\
\code{IndexOutOfBoundsException} & $6637$ & $10.44$ \\
\code{SecurityException}  & $5818$ & $9.15$ \\
\code{NoSuchElementException} & $2392$ & $3.76$ \\
\code{ArithmeticException} & $2338$ & $3.67$ \\
\code{ConcurrentModificationException} & $1889$ & $2.97$ \\
\code{DOMException} & $1024$ & $1.61$ \\
\code{ArrayStoreException} & $279$ & $0.43$ \\
\code{MissingResourceException} & $277$ & $0.43$ \\
% \code{BufferOverFlowException} & $161$ & $0.25$ \\
% \code{NegativeArraySizeException} & $122$ & $0.19$ \\
% \code{BufferUnderFlowException} & $66$ & $0.1$ \\
% \code{LSException} & $64$ &  $0.1$ \\
% \code{MalformedParameterizedTypeException} & $38$ & $0.05$ \\
% \code{CMMException}  & $8$ & $0.01$ \\
% \code{FileSystemNotFoundException} & $6$ & $0.009$ \\
% \code{NoSuchMechanismException} & $3$ & $0.0045$ \\
% \code{MirroredTypesException} & $1$ & $0.0015$
\end{tabular}
\caption{Top $10$ runtime exceptions from stackoverflow~\cite{stackoverflow}.}
\label{tab:stackoverlow}
% }
\end{table}

We have analyzed data from stack overflow and we looked for \java\ runtime
exception which are discussed most frequently. In the
table~\ref{tab:stackoverlow}, the data we find is tabulated along with their
occurrences and percentages.

From the table it is clear that null pointer exception in \java\ is not only the
most frequent but also the most dominant runtime exception having share of more
than $50$.
}

\ignore{
\lstset{language=Java, caption=Bug reproduction of code
snippet\ref{snippet:exampleRepairing}, label = snippet:exampleRepairing}
\begin{figure}[t]
\begin{lstlisting}
String path = "/foo.xml";
String s = ApacheBug.getPathNoEndSeparator(path);
\end{lstlisting}
\end{figure}
}


\ignore{
\lstset{language=Java, caption=Example of repairing technique on Appache Commons
Library in \code{fileUtils}, label = snippet:exampleRepairing2}
\begin{figure}[t]
\begin{lstlisting}
public static String getPathNoEndSeparator(String filename) {
return doGetPath(filename, 0);
}
private static String doGetPath(String filename, int separatorAdd) {
if (filename == null)
return null;
int prefix = getPrefixLength(filename);
if (prefix < 0)
return null;
int index = indexOfLastSeparator(filename);
if ((prefix >= filename.length()) || (index < 0))
return "";
String temp = null;
try
{
temp = filename.substring(prefix, index + separatorAdd);
}
catch(IndexOutOfBoundsException ex)
{
int length = filename.length;
int t = index + separatorAdd;
temp = filename.substring(getI(prefix,t,length), getJ(prefix,t,length));
}

return temp;
}
\end{lstlisting}
\end{figure}
}

